The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-08-02 paper/paper.tex
typos

\begin{table*}[]
	\begin{tabular}{|l|p{8cm}|c|}
	\hline
	\textbf{Name} & \textbf{Description} & \textbf{Submitters} \\
	\hline
	\textsc{Random} & Random assignment (control method)  & Organizers \\
	\textsc{IBandOnly} & i-band only (control method)  & Organizers \\
	\textsc{RandomForest} & A collection of individual decision trees & Organizers \\
	\textsc{LSTM} & Long Short-Term Memory neural network & CRB, BF, GT, ESC, EJG \\
	\textsc{AutokerasLSTM}\tablenotemark{a} & Automaticaly configured LSTM variant. & CRB, BF, GT, ESC, EJG \\
	\textsc{LGBM} & Light Gradient Boosted Machine & CRB, BF, GT, ESC, EJG \\
	\textsc{TCN} & Temporal Convolution Network & CRB, BF, GT, ESC, EJG \\
	\textsc{CNN} & Convolutional Neural Network & CRB, BF, GT, ESC, EJG \\
	\textsc{Ensemble} & Combination of three other network methods & CRB, BF, GT, ESC, EJG \\
	\textsc{SimpleSOM} & Self-Organizing Map & AHW \\
	\textsc{PQNLD} & Extension of {\sc SimpleSom} combining with template-based redshift estimation & AHW \\
	\textsc{UTOPIA} & Nearest-neighbours, optimised in the limit of large representative training sets & AHW \\
	\textsc{ComplexSOM} & Extension of {\sc SimpleSom} with an additional assignment optimization & DA, AHW, AN, EG, AB \\
	\textsc{GPzBinning} & Gaussian Process redshift estimator and binner & PH \\
	\textsc{JaxCNN/JaxResnet} & Two related CNN-based bin edge optimizers & AP \\
	\textsc{NeuralNetwork1/2} & Dense network optimizing bin assignment for two metrics & FL \\
	\textsc{PCACluster} & Principal Component Analysis of fluxes then optimized clustering & DG \\
	\textsc{ZotBin/ZotNet} & Two related neural network methods with a preprocesing normalizing flow & DK \\
	\textsc{FFNN} & Deed-forward neural network & EN \\
	\textsc{FunBins} & Random forest with various nominal bin edge selection & AB \\
	\textsc{MLPQNA} & Multi-layer perceptron & SC, MB \\
	\textsc{Stacked Generalization} & Combination of  Gradient Boosted Trees classifiers with standard Random Forests (50/50) & JEC\\
	\hline
	\end{tabular}
	\caption{Methods entered into the challenge. The algorithms are described more fully in \autoref{app:methods}.}
	\label{tab:entrants}
	\tablenotetext{a}{A technical problem, involving conflicting versions of libraries and incompatible hardware, meant that AutoKerasLSTM could not be run in the final challenge.}
\end{table*}

@@

An illustration of the rank acheived by each method within each challenge configuration and for each metric
is shown in \autoref{fig:rank_grid}.

@@

A comparison of trained-edge and fixed-edge methods on the CosmoDC2 griz scenarios
is shown in Figure \ref{fig:edges}, and the same data normalized against the score acheived
by objects binned in true redshift (i.e. a perfect assigment method) are shown in Figure \ref{fig:metric_grid_dc2_griz}.

@@

In addition to this base functionality, the SimpleSOM method includes a
mechanism for distilling $N_{\rm cell}$ SOM cells into $N_{\rm group}<N_{\rm
cell}$ groups of cells, while maintaining optimal redshift resolution. This is
done by invoking a hierarchical clustering of SOM cells \citep[see Appendix B of
][]{Wright/etal:2020a}, where in this case we combine cells based on the
similarity of the cells' $n(z)$ moments (mean, median, and normalised median absolute
deviation from median) using complete-linkage clustering. The result of this
procedure is the construction of fewer discrete groups of training and reference
data, while not introducing pathological redshift-distribution broadening (as
happens when, e.g., training using a lower resolution SOM and/or clustering
cells based on distances in colour-magnitude space).

@@

\section{Normalized metric scores} \label{app:metric_grids}
Figures \ref{fig:metric_grid_dc2_riz}, \ref{fig:metric_grid_buzzard_griz}, and \ref{fig:metric_grid_buzzard_riz} show metric scores normalized bewteen random assignment and perfect assigment to equal number density bins for CosmoDC2/riz, Buzzard/griz and Buzzard/riz respectively

>>>>

\begin{table*}[]
	\begin{tabular}{|l|p{8cm}|c|}
	\hline
	\textbf{Name} & \textbf{Description} & \textbf{Submitters} \\
	\hline
	\textsc{Random} & Random assignment (control method)  & Organizers \\
	\textsc{IBandOnly} & i-band only (control method)  & Organizers \\
	\textsc{RandomForest} & A collection of individual decision trees & Organizers \\
	\textsc{LSTM} & Long Short-Term Memory neural network & CRB, BF, GT, ESC, EJG \\
	\textsc{AutokerasLSTM}\tablenotemark{a} & Automaticaly configured LSTM variant. & CRB, BF, GT, ESC, EJG \\
	\textsc{LGBM} & Light Gradient Boosted Machine & CRB, BF, GT, ESC, EJG \\
	\textsc{TCN} & Temporal Convolution Network & CRB, BF, GT, ESC, EJG \\
	\textsc{CNN} & Convolutional Neural Network & CRB, BF, GT, ESC, EJG \\
	\textsc{Ensemble} & Combination of three other network methods & CRB, BF, GT, ESC, EJG \\
	\textsc{SimpleSOM} & Self-Organizing Map & AHW \\
	\textsc{PQNLD} & Extension of {\sc SimpleSom} combining with template-based redshift estimation & AHW \\
	\textsc{UTOPIA} & Nearest-neighbours, optimised in the limit of large representative training sets & AHW \\
	\textsc{ComplexSOM} & Extension of {\sc SimpleSom} with an additional assignment optimization & DA, AHW, AN, EG, AB \\
	\textsc{GPzBinning} & Gaussian Process redshift estimator and binner & PH \\
	\textsc{JaxCNN/JaxResnet} & Two related CNN-based bin edge optimizers & AP \\
	\textsc{NeuralNetwork1/2} & Dense network optimizing bin assignment for two metrics & FL \\
	\textsc{PCACluster} & Principal Component Analysis of fluxes then optimized clustering & DG \\
	\textsc{ZotBin/ZotNet} & Two related neural network methods with a preprocesing normalizing flow & DK \\
	\textsc{FFNN} & Feed-forward neural network & EN \\
	\textsc{FunBins} & Random forest with various nominal bin edge selection & AB \\
	\textsc{MLPQNA} & Multi-layer perceptron & SC, MB \\
	\textsc{Stacked Generalization} & Combination of  Gradient Boosted Trees classifiers with standard Random Forests (50/50) & JEC\\
	\hline
	\end{tabular}
	\caption{Methods entered into the challenge. The algorithms are described more fully in \autoref{app:methods}.}
	\label{tab:entrants}
	\tablenotetext{a}{A technical problem, involving conflicting versions of libraries and incompatible hardware, meant that AutoKerasLSTM could not be run in the final challenge.}
\end{table*}

@@

An illustration of the rank achieved by each method within each challenge configuration and for each metric
is shown in \autoref{fig:rank_grid}.

@@

A comparison of trained-edge and fixed-edge methods on the CosmoDC2 griz scenarios
is shown in Figure \ref{fig:edges}, and the same data normalized against the score achieved
by objects binned in true redshift (i.e. a perfect assigment method) are shown in Figure \ref{fig:metric_grid_dc2_griz}.

@@

In addition to this base functionality, the SimpleSOM method includes a
mechanism for distilling $N_{\rm cell}$ SOM cells into $N_{\rm group}<N_{\rm
cell}$ groups of cells, while maintaining optimal redshift resolution. This is
done by invoking a hierarchical clustering of SOM cells \citep[see Appendix B of
][]{Wright/etal:2020a}, where in this case we combine cells based on the
similarity of the cells' $n(z)$ moments (mean, median, and normalized median absolute
deviation from median) using complete-linkage clustering. The result of this
procedure is the construction of fewer discrete groups of training and reference
data, while not introducing pathological redshift-distribution broadening (as
happens when, e.g., training using a lower resolution SOM and/or clustering
cells based on distances in colour-magnitude space).

@@

\section{Normalized metric scores} \label{app:metric_grids}
Figures \ref{fig:metric_grid_dc2_riz}, \ref{fig:metric_grid_buzzard_griz}, and \ref{fig:metric_grid_buzzard_riz} show metric scores normalized between random assignment and perfect assigment to equal number density bins for CosmoDC2/riz, Buzzard/griz and Buzzard/riz respectively
